---
title: "STA 553.HW1"
author: "Zachary Wright"
date: "2/9/2022"
output: html_document
---

#######Code starts on line 145########

output:
  html_document: 
    toc: yes
    number_sections: yes
  html_notebook:
    toc: yes
    number_sections: yes
editor_options:
  chunk_output_type: inline
---


<style type="text/css">

div#TOC li {
    list-style:none;
    background-image:none;
    background-repeat:none;
    background-position:0;
}
h1.title {
  font-size: 24px;
  color: DarkRed;
  text-align: center;
}
h4.author { /* Header 4 - and the author and data headers use this too  */
    font-size: 18px;
  font-family: "Times New Roman", Times, serif;
  color: DarkRed;
  text-align: center;
}
h4.date { /* Header 4 - and the author and data headers use this too  */
  font-size: 18px;
  font-family: "Times New Roman", Times, serif;
  color: DarkBlue;
  text-align: center;
}
h1 { /* Header 3 - and the author and data headers use this too  */
    font-size: 22px;
    font-family: "Times New Roman", Times, serif;
    color: darkred;
    text-align: center;
}
h2 { /* Header 3 - and the author and data headers use this too  */
    font-size: 18px;
    font-family: "Times New Roman", Times, serif;
    color: navy;
    text-align: left;
}

h3 { /* Header 3 - and the author and data headers use this too  */
    font-size: 15px;
    font-family: "Times New Roman", Times, serif;
    color: navy;
    text-align: left;
}

h4 { /* Header 4 - and the author and data headers use this too  */
    font-size: 18px;
    font-family: "Times New Roman", Times, serif;
    color: darkred;
    text-align: left;
}
</style>

```{r setup, include=FALSE}
# code chunk specifies whether the R code, warnings, and output 
# will be included in the output files.
if (!require("tidyverse")) {
   install.packages("tidyverse")
   library(tidyverse)
}
if (!require("knitr")) {
   install.packages("knitr")
   library(knitr)
}
if (!require("cowplot")) {
   install.packages("cowplot")
   library(cowplot)
}
if (!require("latex2exp")) {
   install.packages("latex2exp")
   library(latex2exp)
}
if (!require("plotly")) {
   install.packages("plotly")
   library(plotly)
}
if (!require("gapminder")) {
   install.packages("gapminder")
   library(gapminder)
}
if (!require("png")) {
    install.packages("png")             # Install png package
    library("png")
}
if (!require("RCurl")) {
    install.packages("RCurl")             # Install RCurl package
    library("RCurl")
}
if (!require("colourpicker")) {
    install.packages("colourpicker")              
    library("colourpicker")
}
if (!require("gganimate")) {
    install.packages("gganimate")              
    library("gganimate")
}
if (!require("gifski")) {
    install.packages("gifski")              
    library("gifski")
}
if (!require("magick")) {
    install.packages("magick")              
    library("magick")
}
if (!require("grDevices")) {
    install.packages("grDevices")              
    library("grDevices")
}
if (!require("jpeg")) {
    install.packages("jpeg")              
    library("jpeg")
}
# knitr::opts_knit$set(root.dir = "C:/Users/75CPENG/OneDrive - West Chester University of PA/Documents")
# knitr::opts_knit$set(root.dir = "C:\\STA490\\w05")

knitr::opts_chunk$set(echo = TRUE,       
                      warning = FALSE,   
                      result = TRUE,   
                      message = FALSE)
```



Reads in the Penguin data set and lists out all the data.
```{r}
pengdata = read.csv("https://raw.githubusercontent.com/zackwright27/sta553/main/data/w02-penguins.csv")
head(pengdata)
```



```{r, fig.align='center', fig.cap="Scatter plot of sepal length and sepal width"}
plot(pengdata$bill_length_mm, pengdata$flipper_length_mm, 
     xlab = "Bill Length in mm", 
     ylab = "Flipper Length in mm", 
     main = "Scatter Plot: Bill Length vs. Flipper Length")


bill.length = pengdata$bill_length_mm
flipper.length = pengdata$flipper_length_mm
species = pengdata$species
body.mass = pengdata$body_mass_g/1000


## identifying the ID of Virginica
virginca.id = which(species=="Adelie")  # value are case sensitive!
setosa.id = which(species=="Gentoo")
versicolor.id = which(species=="Chinstrap")


## making an empty plot: type = "n" ==> no point
plot(bill.length, flipper.length, main = "Bill Length vs Flipper Length", type = "n")


##
points(bill.length[virginca.id], flipper.length[virginca.id], pch = 18, col = "purple")
points(bill.length[setosa.id], flipper.length[setosa.id], pch = 19, col = "orange")
points(bill.length[versicolor.id], flipper.length[versicolor.id], pch = 20, col = "green")
legend("topleft", c("Adelie", "Gentoo", "Chinstrap"), 
                  col=c("purple", "orange", "green"),
                  pch=c(18, 19, 20))


## color code
col.code = c(alpha("red",0.5),alpha("blue",0.5),alpha("cyan",0.5))
## making an empty plot: type = "n" ==> no point
plot(bill.length, flipper.length, main = "Bill Length vs Flipper Length", type = "n")
## change the point size based body mass
points(bill.length[virginca.id], flipper.length[virginca.id], 
       pch = 19, col = col.code[1], cex = body.mass[virginca.id])
points(bill.length[setosa.id], flipper.length[setosa.id], 
       pch = 19, col = col.code[2], cex = body.mass[setosa.id])
points(bill.length[versicolor.id], flipper.length[versicolor.id], 
       pch = 19, col = col.code[3], cex = body.mass[versicolor.id])
legend("topleft", c("virginica", "setosa", "versicolor"), 
                  col=col.code,
                  pch=c(19, 19, 19))



penguin.jpeg <- "https://raw.githubusercontent.com/zackwright27/sta553/main/data/Penguin%20for%20STA%20553.jpeg"
my_peng <- readJPEG(getURLContent(penguin.jpeg))
raster.peng <- as.raster(my_peng) 
rasterImage(raster.peng,3,1.5,3.5,2.4)
text(4.25, 1.25, "The size is proportional to body mass", col = "blue", cex = 0.5)
```